Perturbing SU($n$)-symmetric interactions

### 2019-12-06 soc_squeezing/collective_paper/review/response.tex

\documentclass[preprint,superscriptaddress]{revtex4-2}

% linking references
\usepackage{hyperref}
\hypersetup{
  breaklinks=true,
  colorlinks=true,
  linkcolor=blue,
  urlcolor=cyan,
}

%%% symbols, notations, etc.
\usepackage{physics,braket,bm,commath,amssymb}
\renewcommand{\t}{\text} % text in math mode
\newcommand{\f}[2]{\dfrac{#1}{#2}} % shorthand for fractions
\newcommand{\p}[1]{\left( #1 \right)} % parenthesis
\renewcommand{\sp}[1]{\left[ #1 \right]} % square parenthesis
\renewcommand{\v}{\bm} % bold vectors
\newcommand{\uv}[1]{\bm{\hat{#1}}} % unit vectors

\renewcommand{\abs}[1]{\lvert #1 \rvert}

\newcommand{\bk}{\braket} % shorthand for braket notation
\newcommand{\Bk}{\Braket}

\newcommand{\ul}{\underline} % shorthand for underline

\newcommand{\A}{\mathcal{A}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathcal{E}}
\newcommand{\J}{\mathcal{J}}
\renewcommand{\O}{\mathcal{O}}
\newcommand{\Q}{\mathcal{Q}}
\renewcommand{\S}{\mathcal{S}}
\newcommand{\U}{\mathcal{U}}

\newcommand{\C}{\mathbb{C}}
\newcommand{\N}{\mathbb{N}}

\newcommand{\z}{\text{z}}
\newcommand{\x}{\text{x}}
\newcommand{\y}{\text{y}}
\newcommand{\Z}{\text{Z}}
\newcommand{\X}{\text{X}}
\newcommand{\Y}{\text{Y}}
\newcommand{\bmu}{{\bar\mu}}
\newcommand{\bnu}{{\bar\nu}}

\usepackage{dsfont} % for identity operator
\newcommand{\1}{\mathds{1}}

\newcommand{\up}{\uparrow}
\newcommand{\dn}{\downarrow}

\renewcommand{\a}{\alpha} % free index
\renewcommand{\b}{\beta} % free index

%%% figures
\usepackage{graphicx} % for figures
\usepackage[caption=false]{subfig} % subfigures (via \subfloat[]{})
\newcommand{\sref}[1]{\protect\subref{#1}} % for referencing subfigures
\graphicspath{{./figures/}} % set path for all figures

% remove extra white space inside enumerate environments
\usepackage[inline]{enumitem}
\setenumerate{label=(\roman*)}
\setlist[enumerate]{leftmargin=*}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1ex}

% for colored text
\usepackage[dvipsnames]{xcolor}
\newcommand{\blue}[1]{{\color{blue} #1}}
\newcommand{\red}[1]{{\color{red} #1}}
\newcommand{\green}[1]{{\color{ForestGreen} #1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

Dear Editors,

Please find attached our revised manuscript AJ11834, titled
``Short-time expansion of Heisenberg operators in open collective
quantum spin systems'', for consideration for publication in Physical
Review A.  Below, we address the questions and comments made by our
referees, and detail the corresponding changes that we have made to
our manuscript.  We hope that our responses and changes address the
referees' questions to a satisfactory degree, leaving no more
outstanding questions or concerns about our work.

Excerpts from the referee reports are written in \blue{blue}, excerpts
from the previous version of our manuscript are written in \red{red},
and excerpts from the revised version of our manuscript are written in
\green{green}.  Unless explicitly stated otherwise, all equation
numbers, page numbers, etc.~refer to those in the revised manuscript.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{First referee}

\begin{enumerate}
\item Concerning the first referee's summary and comments:

  \blue{The authors have studied open collective spin systems with
    generic Markovian decoherence and presented a new method to
    calculate short-time correlators. The method is based on an
    expansion of Heisenberg operators and truncation of it for short
    times (TST). The number of particles that the presented method can
    deal with are shown to be rather high. The method is meant to work
    well with highly-correlated systems. Spin squeezing, two-time
    correlation functions, and out-of-time-ordered correlators are
    calculated as an application of the new method. As technical parts
    of the paper, authors calculate all the ingredients, e.g., the
    structure constants of a collective spin operator algebra, which
    are necessary to apply the method.}

  \blue{Although the developed method works only at short times, it
    can be fruitful for applications in the field of quantum
    metrology. One of the key points that makes the paper interesting
    is the capability of the TST expansion to compute the spin
    correlators in a regime (strong correlations) that other methods
    cannot practically access. In the regime that it works, the method
    is efficient and very promising for future applications.}

  \blue{Overall, the paper is well written and the presented method
    and following results deserve publication in Phys.~Rev.~A. In
    particular, I expect it to be utilized in the spin squeezed
    systems. I just have the following question:}

  We thank the referee for their summary of our work, and for the
  conclusion that our results deserve publication in Phys.~Rev.~A.  We
  similarly hope that our method finds useful applications in spin
  squeezed systems, as well as others.  We address the referee's
  question below.

\item Concerning the first referee's question:

  \blue{In the last paragraph of page 4, which continues to page 5,
    authors explain how unphysical result can be marked by and
    unphysical squeezing parameter. In the same paragraph authors list
    three possible mechanisms for breakdown. Is there a fundamental
    relationship between all of the three breakdown mechanisms and the
    value of the squeezing parameter? Asked differently, could it be
    possible that one of the three breakdown mechanisms happens
    without the squeezing parameter going unphysical?}

  The referee brings up a good question about diagnosing the breakdown
  of our method (TST).  In fact, there is {\it no} fundamental
  relationship between the breakdown of TST and an unphysical
  squeezing parameter ($\xi^2<0$), and it {\it is} possible for
  breakdown to occur without the squeezing parameter going unphysical.
  Instead, there is a direct relationship between the breakdown of TST
  and the value of individual correlators $\bk{\hat S_{\v n}}$ that
  are used to compute the squeezing parameter $\xi^2$.  The breakdown
  of TST affects (non-negligible) contributions to correlators
  $\bk{\hat\S_{\v n}}$ that grow with the time $t$ raised to some
  large power, so after breakdown these correlators rapidly take on
  unphysical values.  It is often the case that unphysical correlators
  will lead to an unphysical squeezing parameter, but not always.  The
  breakdown of TST should therefore be diagnosed by inspecting the
  correlators used to compute the squeezing parameter, rather than by
  inspecting the squeezing parameter itself.

  In order to clarify the diagnosis of breakdown for the TST
  expansion, we have rearranged and added text to the paragraph in
  question, replacing (end of page 4 through some of page 5 in the old
  text):

  \red{The main lesson from Figure 1 is that the TST expansion yields
    essentially exact results right up until a sudden and drastic
    departure that can be diagnosed by inspection.  {\bf The breakdown
      of the TST expansion in Figure 1 is marked by an unphysical
      squeezing parameter $\xi^2<0$, which occurs due to individual
      correlators taking unphysical values with
      $\abs{\bk{\hat\S_{\v n}\p{t}}}\gtrsim S^{\abs{\v n}}$.  Going up
      through order $M=70$ in the TST expansion does not significantly
      increase the breakdown time $t_{\t{break}}^{(M)}$, and in some
      cases even shortens $t_{\t{break}}^{(M)}$.}  The sudden and
    drastic departure from virtually exact results is consistent with
    the limitations of the TST expansion discussed at the end of
    Section II.  Specifically, we identify three possible mechanisms
    for breakdown:
    \begin{enumerate*}
    \item a rapid growth in the order $M$ necessary for the TST
      expansion to converge,
    \item the growth of numerical errors in excessively large terms of
      the TST expansion, and
    \item the formal breakdown of the perturbative expansion in the
      time $t$.
    \end{enumerate*}
    In all of these cases, a detailed cancellation eventually ceases
    to occur between large terms at high orders in the TST expansion.
    These large terms grow with the time $t$ raised to some large
    power (as high as $M$), and therefore rapidly yield wildly
    unphysical results.  In contrast to other approximate methods such
    as the cumulant expansion[58], the TST expansion can thus diagnose
    its own breakdown, which is an important feature when working in
    parameter regimes that are inaccessible via other means to compute
    correlators.}

  by (top of page 5 in the new text):

  \green{The main lesson from Figure 1 is that the TST expansion
    yields essentially exact results right up until a sudden and
    drastic departure that can be diagnosed by inspection.  {\bf The
      breakdown of the TST expansion in Figure 1 induces an unphysical
      squeezing parameter $\xi^2<0$.  In general, however, there is no
      fundamental relationship between the breakdown of the TST
      expansion and the conditions for a physical squeezing parameter
      $\xi^2$.  A proper diagnosis of breakdown therefore requires
      inspection of the correlators $\bk{\hat\S_{\v n}\p{t}}$ used to
      compute the squeezing parameter $\xi^2$, which upon breakdown
      will rapidly take unphysical values with
      $\abs{\bk{\hat\S_{\v n}\p{t}}}\gtrsim S^{\abs{\v n}}$.}  The
    sudden and drastic departure from virtually exact results is
    consistent with the limitations of the TST expansion discussed at
    the end of Section II.  Specifically, we identify three possible
    mechanisms for breakdown:
    \begin{enumerate*}
    \item a rapid growth in the order $M$ necessary for the TST
      expansion to converge,
    \item the growth of numerical errors in excessively large terms of
      the TST expansion, and
    \item the formal breakdown of the perturbative expansion in the
      time $t$.
    \end{enumerate*}
    In all of these cases, a detailed cancellation eventually ceases
    to occur between large terms at high orders in the TST expansion.
    These large terms grow with the time $t$ raised to some large
    power (as high as $M$), and therefore rapidly yield wildly
    unphysical results.  In contrast to other approximate methods such
    as the cumulant expansion[58], the TST expansion can thus diagnose
    its own breakdown, which is an important feature when working in
    parameter regimes that are inaccessible via other means to compute
    correlators.  {\bf Note that, due to the breakdown mechanisms of
      the TST expansion, going up through order $M=70$ does not
      significantly increase the breakdown time $t_{\t{break}}^{(M)}$
      in Figure 1, and in some cases even shortens
      $t_{\t{break}}^{(M)}$.}}

  Note that we used of bold text to help identify the changes above;
  the manuscript itself does not make these changes bold.  We hope
  that these changes clarify the relationship between breakdown of the
  TST expansion and an unphysical squeezing parameter.

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Second referee}

\begin{enumerate}
\item Concerning the second referee's summary and comments:

  \blue{In this work, the authors compute the dynamics of collective
    spin systems with decoherence via uncorrelated decay of individual
    spins by solving the operators’ Heisenberg’s equation of motion
    approximately.  It is carried out in the following way: Heisenberg
    operators are formally expanded into a Taylor series, which is
    then truncated to a finite order for short evolution times. The
    authors benchmark the method by computing spin squeezing, two-time
    correlation functions, and out-of-time-ordered correlators.

    The paper is clearly written, and the derivations appear to be
    sound.  However, there are some points need to be clarified before
    this paper can be accepted for publication.}

  We thank the referee for their succinct summary of our method, and
  for the the recognition that our manuscript is well written, and our
  derivations sound.  We address the refere's points below, and hope
  that the corresponding changes to our manuscript deem our work
  acceptable for publication in Physical Review A.

\item Concerning the first point, about novelty:

  \blue{1. The authors declare that they present a ‘new’
    method. However, it seems that the method as described resembles
    (if not the same as) the well-known Mori formalism, or memory
    function method, developed by Mori, Berne, Lee, Grigolini and
    others [see for example H.~Mori, Prog.~Theor.~Phys.~34 399
    (1965); James F Annett, et al.~Condens.~Matter 6, 645(1994)],
    where the Liouvillian superoperator is used to provide a compact
    representation of the time evolution of operators under
    Heisenberg’s equation of motion, and followed up with a continued
    fraction expansion. I hope the authors could acknowledge these
    previous studies and be careful with the claiming of ‘new’
    method.}

  We thank the referee for drawing our attention to the Mori formalism
  (\url{https://doi.org/10/cgtkbb}) and the related work by Annett et
  al.~(\url{https://doi.org/10/d79ngr}).  Indeed, there are some
  interesting connections between these works and ours, as pointed out
  by the referee.  For example, all of these methods rely on some sort
  of formal solution to the equations of motion for Heisenberg
  operators.  Nonetheless, we strongly believe that our methods are
  substantively distinct from those of these past works, and expand on
  some differences below.  In acknowledgment of the resemblance and
  connections to past works, however, we have also followed the
  referee's suggestion and changed all instances of ``\red{a new
    method}'' in our manuscript to ``\green{an efficient method}''.
  We have also added references to the Mori formalism and follow-up
  works (outlined below).

  At a high level, the truncated short-time (TST) expansion for a
  Heisenberg operator, Eq.~(10) in our manuscript, essentially
  involves only products of (i) initial-time expectation values of
  operators chosen from a fixed basis, and (ii) matrix elements of the
  time derivative operator $T$ (essentially the Liouvillian), as well
  as powers of $T$.  In order to evaluate the TST expansion, our
  method makes use of the structure constants of a collective spin
  operator algebra.  The Mori formalism, meanwhile, arrives at an
  expansion of Heisenberg operators (see Eq.~2.29 of
  \url{https://doi.org/10/cgtkbb}) that involves (i) Laplace
  transforms, (ii) operators, $f_j$, that are constructed recursively
  from the initial Heisenberg operator of interest, and (iii)
  coefficients, $C_j$, that are defined using the operators $f_j$ and
  additional Laplace transforms.  In order to evaluate this expansion,
  the Mori formalism provides a continued-fraction representation of
  the coefficients $C_j$.  Perhaps additional work might illuminate
  the connections between these two methods, but at face value they
  are quite different.

  Some of the work by Annett et al.~in \url{https://doi.org/10/d79ngr}
  has a closer resemblance to ours, in that Eq.~(25) therein is,
  similar to the TST expansion, a series expansion organized in powers
  of the time $t$.  Even here, however, Eq.~(25) concerns only one
  component of an (initially localized) Heisenberg operator $Q(t)$,
  namely the projection of $Q(t)$ onto $Q(0)$.  Furthermore, the
  solution of Eq.~(25) involves resolving $Q(t)$ into frequency
  components $R(\omega)$, representing the resolvents $R(\omega)$ by a
  continued fraction with some free parameters $\set{a_n,b_n}$, and
  then solving for the parameters $\set{a_n,b_n}$.  Our TST expansion
  considers explicitly non-local operators, solves for the entirety of
  these operators (as opposed to only one component), and involves
  neither frequency components nor continued fractions.  We hope that
  these considerations clarify how the TST expansion is distinct from
  past works.

  Despite these differences, we acknowledge that there may be some
  interesting connections between the above works and ours, and that
  investigating these connections may lead to a refinement of our
  work.  We have therefore changed the following sentence in the
  introduction (top left of page 2):

  \red{Our method is based on a short-time expansion of exact
    solutions to the equations of motion for Heisenberg operators.
    Evaluating this expansion requires ...}

  to:

  \green{Our method is based on a formal solution to the equations of
    motion for Heisenberg operators, thereby bearing some resemblance
    to the Mori formalism[59] and related work[60].  Specifically, we
    expand a formal solution for a Heisenberg operator into a Taylor
    series whose truncation can yield negligible error at sufficiently
    short times.  Evaluating the resulting expansion requires ...}

  We have also added a reference to these works to the discussion of
  the limitations of the TST expansion at the end of the theory
  section of our manuscript (right column of page 3), changing the
  sentence:

  \red{Precisely characterizing the implications of these last two
    considerations for the TST expansion requires additional analysis
    that we defer to future work.}

  to:

  \green{Precisely characterizing the implications of these last two
    considerations for the TST expansion requires additional analysis
    that we defer to future work, which may benefit from an
    investigation of the connections between the TST expansion and
    past works related to the Mori formalism[59, 60].}

  We hope that the referee considers these additions a sufficient
  acknowledgment of the Mori formalism and related work.

\item Concerning the second question, about decoherence:

  \blue{2. I am not sure if the paper properly takes into account
    previous results about the influence of decoherence on spin
    squeezing. First, there exists many mechanisms for decoherence,
    while decoherence considered in this paper is due to uncorrelated
    decay of individual spins. This is not clarified in the
    introduction. In fact, atom loss represents an important mechanism
    of decoherence in spin squeezing experiments, but is not
    considered in this paper. Could the method studied here also be
    applied to atom loss? It would be helpful if this point is
    mentioned. Second, for the specific decoherence model considered,
    the authors only cite a few studies about the influence of such
    decoherence on spin squeezing from one-axis twisting (OAT). There
    are many studies about the effect of decoherence on spin
    squeezing.}

  The referee makes a fair point that we claim to present a method for
  simulating ``generic'' Markovian decoherence, when in fact we only
  address certain (typical) forms of Markovian decoherence.  To avoid
  misleading readers about the contents of our paper, we have
  therefore replaced the words ``\red{generic Markovian decoherence}''
  by ``\green{typical forms of Markovian decoherence}'' in the
  abstract, as well as the last paragraph of the introduction.

  We would like to point out that our work {\it does} address more
  than just uncorrelated decay of individual spins: we also address
  uncorrelated excitation and dephasing of individual spins, as well
  as arbitrary coherent or incoherent combinations of these processes.
  Similarly, we provide all ingredients necessary to account for
  arbitrary combinations of {\it collective} decay, excitation, and
  dephasing in Appendices D-G, as mentioned in the paragraph below
  Eq.~(4) of our manuscript.

  The referee is correct, though, that our original manuscript does
  not discuss atom loss, which is an important decoherence mechanism
  in some experimental realizations of collective spin models.  We
  have therefore added the following discussion about atom loss to the
  theory section our manuscript (bottom right of page 2):

### 2019-12-11 collective_sun/sun_perturbation.tex
simplified two-body eigenvalue problem in the case of translational invariance

\newcommand{\EE}{\mathbb{E}}
\newcommand{\RR}{\mathbb{R}}
\renewcommand{\SS}{\mathbb{S}}
\newcommand{\ZZ}{\mathbb{Z}}

\newcommand{\PP}{\mathbb{Z}}

\newcommand{\FS}{\text{FS}}
\newcommand{\EQFS}{=_{\text{FS}}}
\newcommand{\col}{\underline}

\DeclareMathOperator{\sign}{sign}
\DeclareMathOperator{\cov}{cov}
\let\var\relax
\DeclareMathOperator{\var}{var}
\DeclareMathOperator{\diag}{diag}
\let\flat\relax
\DeclareMathOperator{\flat}{flat}
\DeclareMathOperator{\counts}{counts}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Single-body perturbations}

To compute the effective Hamiltonian induced by the single-body
perturbation $\V_1$, we use the permutational symmetry of the
ground-state manifold to simplify
\begin{align}
  H_1^{(1)} = \sum_p v_p \P_0 X_p \P_0
  = \sum_p v_p \P_0 X_0 \P_0 \EQFS \bar v \col{X},
  \label{eq:H_1_1}
\end{align}
where $\EQFS$ denotes equality under a restriction to the fully
symmetric manifold $\M_0$, and
\begin{align}
  \bar v \equiv \f1N \sum_p v_p,
  &&
  \col{X} \equiv \sum_p X_p.
\end{align}
In order to compute the second order effective Hamiltonian
$H_1^{(2)}$, we first choose an arbitrary fully symmetric state
$\ket\psi\in\M_0$ and expand (see Appendix \ref{sec:H_V1_psi}):
\begin{align}
  H_0 \V_1 \ket\psi
  = E_0 \V_1 \ket\psi
  + \p{\sum_{p,q} h_{pq} v_p X_q - \sum_q h_q v_q X_q} \ket\psi,
  \label{eq:H_V1_psi}
\end{align}
where $h_q\equiv\sum_p h_{pq}$ is the net interaction energy
associated with spin $p$.  We thus find that the vector $\V_1\ket\psi$
is an eigenvector of the interaction Hamiltonian $H_0$ if the
coefficients $\v v$ satisfy
\begin{align}
  \p{\m h - \diag\v h}\c\v v = \Delta\p{\v v} \v v,
  \label{eq:cond_1}
\end{align}
where $\v h,\m h$ are respectively a vector and matrix of all
$h_p,h_{pq}$; $\diag\v h$ is a matrix with $\v h$ on the diagonal and
zeros everywhere else; and $\Delta\p{\v v}$ is some constant that may
depend on $\v v$.  If we {\it construct} a perturbation
$\V_1\p{\v v_\Delta}$ with coefficients $\v v_\Delta$ that satisfy
\eqref{eq:cond_1} with eigenvalue $\Delta$, then
\begin{align}
  H_0 \V_1\p{\v v_\Delta} \ket\psi
  = \p{E_0 + \Delta} \V_1\p{\v v_\Delta} \ket\psi.
\end{align}
Interestingly, the energy of the (unnormalized) state
$\V_1\p{\v v_\Delta}\ket\psi$ depends only on the coefficients
$\v v_\Delta$, and is entirely independent of the state $\ket\psi$ or
choice of single-spin trace-zero operator $X$ used to build $\V_1$ in
\eqref{eq:perturbations}.  Finding operators $\V_1\p{\v v_\Delta}$
that generate eigenvectors of the interaction Hamiltonian $H_0$ when
they act on fully symmetric states $\ket\psi$ thus reduces to finding
eigenvectors $\v v_\Delta$ of the interaction matrix $\m h-\diag\v h$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Two-body perturbations}

The first-order effective Hamiltonian $H_2^{(1)}$ induced on the fully
symmetric manifold $\M_0$ by the two-body perturbation $\V_2$ in
\eqref{eq:perturbations} is simply the restriction of $\V_2$ onto
$\M_0$ (see Appendix \ref{sec:PXYP}):
\begin{align}
  H_2^{(1)}
  = \P_0 \V_2 \P_0
  \EQFS \f12 \bar w \p{\col{X}\odot\col{Y} - \col{X\odot Y}},
\end{align}
where $A\odot B\equiv\p{AB+BA}/2$ is a symmetrized product of $A$ and
$B$; and
\begin{align}
  \bar w \equiv {N\choose 2}^{-1} \sum_{p<q} w_{pq},
  &&
  \col{X} \equiv \sum_p X_p,
  &&
  \col{Y} \equiv \sum_p Y_p,
  &&
  \col{X\odot Y} \equiv \sum_p X_p\odot Y_p.
\end{align}
In order to compute the second-order effective Hamiltonian
$H_2^{(2)}$, as before we pick an arbitrary fully symmetric state
$\ket\psi\in\M_0$ and expand (see Appendix \ref{sec:H_V2_psi})
\begin{align}
  H_0 \V_2 \ket\psi
  = E_0 \V_2 \ket\psi
  + \sum_{k,\ell} \bar h_{k\ell} w_{k\ell} X_k Y_\ell \ket\psi
  + \f12 \sum_{k\ne\ell} \sum_q \p{h_{kq} w_{q\ell} + w_{kq} h_{q\ell}}
  X_k Y_\ell \ket\psi,
  \label{eq:H_V2_psi}
\end{align}
where to keep notation compact, we define
\begin{align}
  \bar h_{k\ell} \equiv h_{k\ell} - \f12\p{h_k + h_\ell},
  &&
  h_k \equiv \sum_\ell h_{k\ell}.
\end{align}
We thus find that the vector $\V_2\ket\psi$ is an eigenvector of the
interaction Hamiltonian $H_0$ if the coefficients $\m w$ satisfy
\begin{align}
  2\bar{\m h} \circ \m w + \m h\c\m w + \m w\c\m h
  = \Delta\p{\m w} \m w,
  \label{eq:cond_2}
\end{align}
where $\m w,\m h,\bar{\m h}$ are matrices of all
$w_{k\ell},h_{k\ell},\bar h_{k\ell}$; $\bar{\m h} \circ \m w$ is an
element-wise (Hadamard) product of $\bar{\m h}$ and $\m w$, i.e.~with
matrix elements $\bar h_{k\ell} w_{k\ell}$; and $\Delta\p{\m w}$ is
some constant that may depend on $\m w$.

We can recast the condition in \eqref{eq:cond_2} as an eigenvalue
problem by writing the coefficient matrix $\m w$ as a vector
$\v{\m w}$ in $\RR^N\times\RR^N$,
\begin{align}
  \m w = \sum_{p,q} w_{pq} \op{p}{q}
  \to \v{\m w} \equiv \flat\m w \equiv \sum_{p,q} w_{pq} \ket{pq},
\end{align}
where $\flat\m m$ is a flattening of the matrix $\m m$ into a vector
$\vec{\m m}$, and defining the matrix
\begin{align}
  \check{\m h}
  \equiv 2\diag\p{\flat\bar{\m h}}
  + \m h\otimes\1_N + \1_N\otimes\m h
  = 2 \sum_{p,q} \bar h_{pq} \op{pq}
  + \sum_{p,q,\ell} h_{pq} \p{\op{p\ell}{q\ell} + \op{\ell p}{\ell q}},
  \label{eq:h_super_mat}
\end{align}
where $\1_D$ is a $D\times D$ identity matrix.  The condition in
\eqref{eq:cond_2} is then equivalently the eigenvalue equation
\begin{align}
  \p{\check{\m d} \c \check{\m h} \c \check{\m d}} \c \v{\m w}
  = \Delta\p{\m w} \v{\m w},
  &&
  \check{\m d} \equiv \1_{N^2} - \sum_\ell \op{\ell\ell},
  \label{eq:cond_2_eig}
\end{align}
where $\check{\m d}$ annihilates the diagonal part of a (flattened)
matrix it acts on, while keeping the off-diagonal components the same.
We conjugate $\check{\m h}$ by $\check{\m d}$ to enforce that its
eigenvectors $\v{\m w}$ correspond to matrices $\m w$ with zeros on
the diagonal, i.e.~$w_{pp}=0$.

Both numerical experiments and physical arguments suggest that the
$N^2\times N^2$ matrix $\check{\m d} \c \check{\m h} \c \check{\m d}$
is highly degenerate, which means that we might be able to simplify
\eqref{eq:cond_2_eig} even further.  We defer this simplification to
future work, and for now bear the (large) computational cost of
diagonalizing a $N^2\times N^2$ matrix.

>>>>

\newcommand{\EE}{\mathbb{E}}
\newcommand{\RR}{\mathbb{R}}
\renewcommand{\SS}{\mathbb{S}}
\newcommand{\VV}{\mathbb{V}}
\newcommand{\ZZ}{\mathbb{Z}}

\newcommand{\FS}{\text{FS}}
\newcommand{\EQFS}{=_{\text{FS}}}
\newcommand{\col}{\overline}

\DeclareMathOperator{\sign}{sign}
\DeclareMathOperator{\cov}{cov}
\let\var\oldvar
\DeclareMathOperator{\var}{var}
\DeclareMathOperator{\diag}{diag}
\let\flat\oldflat
\DeclareMathOperator{\flat}{flat}
\DeclareMathOperator{\counts}{counts}
\newcommand{\flatvec}{\underline\flat\,}
\newcommand{\ul}{\underline}

\usepackage{accents}
\newcommand{\ut}{\undertilde}

\newcommand{\floor}[1]{\lfloor{#1}\rfloor}
\newcommand{\ceil}[1]{\lceil{#1}\rceil}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Single-body perturbations}
\label{sec:single_body}

To compute the effective Hamiltonian induced by the single-body
perturbation $\V_1$, we use the permutational symmetry of the
ground-state manifold to simplify
\begin{align}
  H_1^{(1)} = \sum_p v_p \P_0 X_p \P_0
  = \sum_p v_p \P_0 X_0 \P_0 \EQFS \bar v \col{X},
  \label{eq:H_1_1}
\end{align}
where $\EQFS$ denotes equality under a restriction to the fully
symmetric manifold $\M_0$, and
\begin{align}
  \bar v \equiv \f1N \sum_p v_p,
  &&
  \col{X} \equiv \sum_p X_p.
\end{align}
In order to compute the second order effective Hamiltonian
$H_1^{(2)}$, we first choose an arbitrary fully symmetric state
$\ket\psi\in\M_0$ and expand (see Appendix \ref{sec:H_V1_psi}):
\begin{align}
  H_0 \V_1 \ket\psi
  = E_0 \V_1 \ket\psi
  + \p{\sum_{p,q} h_{pq} v_p X_q - \sum_q h_q v_q X_q} \ket\psi,
  \label{eq:H_V1_psi}
\end{align}
where $h_q\equiv\sum_p h_{pq}$ is the net interaction energy
associated with spin $p$.  We thus find that the vector $\V_1\ket\psi$
is an eigenvector of the interaction Hamiltonian $H_0$ if the
coefficients $\v v$ satisfy
\begin{align}
  \p{\m h - \diag\v h}\c\v v = \Delta\p{\v v} \v v,
  \label{eq:cond_1}
\end{align}
where $\v h,\m h$ are respectively a vector and matrix of all
$h_p,h_{pq}$; $\diag\v h$ is a matrix with $\v h$ on the diagonal and
zeros everywhere else; and $\Delta\p{\v v}$ is some constant that may
depend on $\v v$.  Solving the general eigenvalue problem in
\eqref{eq:cond_1} requires diagonalizing an $N\times N$ matrix.  When
the interaction Hamiltonian $H_0$ is translationally invariant,
however, this eigenvalue problem can be solved analytically; we
provide the corresponding solution in Appendix \ref{sec:trans_inv}.

If we {\it construct} a perturbation $\V_1\p{\v v_\Delta}$ with
coefficients $\v v_\Delta$ that satisfy \eqref{eq:cond_1} with
eigenvalue $\Delta$, then
\begin{align}
  H_0 \V_1\p{\v v_\Delta} \ket\psi
  = \p{E_0 + \Delta} \V_1\p{\v v_\Delta} \ket\psi.
\end{align}
Interestingly, the energy of the (unnormalized) state
$\V_1\p{\v v_\Delta}\ket\psi$ depends only on the coefficients
$\v v_\Delta$, and is entirely independent of the state $\ket\psi$ or
choice of single-spin trace-zero operator $X$ used to build $\V_1$ in
\eqref{eq:perturbations}.  Finding operators $\V_1\p{\v v_\Delta}$
that generate eigenvectors of the interaction Hamiltonian $H_0$ when
they act on fully symmetric states $\ket\psi$ thus reduces to finding
eigenvectors $\v v_\Delta$ of the interaction matrix $\m h-\diag\v h$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Two-body perturbations}
\label{sec:two_body}

The first-order effective Hamiltonian $H_2^{(1)}$ induced on the fully
symmetric manifold $\M_0$ by the two-body perturbation $\V_2$ in
\eqref{eq:perturbations} is simply the restriction of $\V_2$ onto
$\M_0$ (see Appendix \ref{sec:PXYP}):
\begin{align}
  H_2^{(1)}
  = \P_0 \V_2 \P_0
  \EQFS \f12 \bar w \p{\col{X}\odot\col{Y} - \col{X\odot Y}},
\end{align}
where $A\odot B\equiv\p{AB+BA}/2$ is a symmetrized product of $A$ and
$B$; and
\begin{align}
  \bar w \equiv {N\choose 2}^{-1} \sum_{p<q} w_{pq},
  &&
  \col{X} \equiv \sum_p X_p,
  &&
  \col{Y} \equiv \sum_p Y_p,
  &&
  \col{X\odot Y} \equiv \sum_p X_p\odot Y_p.
\end{align}
In order to compute the second-order effective Hamiltonian
$H_2^{(2)}$, as before we pick an arbitrary fully symmetric state
$\ket\psi\in\M_0$ and expand (see Appendix \ref{sec:H_V2_psi})
\begin{align}
  H_0 \V_2 \ket\psi
  = E_0 \V_2 \ket\psi
  + \f12 \sum_{p\ne q} \sp{2\bar h_{pq} w_{pq}
    + \sum_k \p{h_{pk} w_{kq} + w_{pk} h_{kq}}}
  X_p Y_q \ket\psi,
  \label{eq:H_V2_psi}
\end{align}
where to keep notation compact, we define
\begin{align}
  \bar h_{pq} \equiv h_{pq} - \f12\p{h_p + h_q},
  &&
  h_p \equiv \sum_q h_{pq}.
\end{align}
We thus find that the vector $\V_2\ket\psi$ is an eigenvector of the
interaction Hamiltonian $H_0$ if the coefficients $\m w$ satisfy
\begin{align}
  2 \bar h_{pq} w_{pq}
  + \sum_{k\notin\set{p,q}} \p{h_{pk} w_{kq} + w_{pk} h_{kq}}
  = \Delta\p{\m w} w_{pq},
  \label{eq:cond_2}
\end{align}
where $\Delta\p{\m w}$ is some constant that may depend on $\m w$, and
for clarity we explicitly exclude terms with $k\in\set{p,q}$ that
vanish due to the fact that $\m h$ and $\m w$ are zero on the
diagonal.  We can recast the condition in \eqref{eq:cond_2} as an
eigenvalue problem by writing the coefficient matrix $\m w$ as a
vector $\v{\m w}\in\RR^{N\choose 2}$,
\begin{align}
  \m w = \sum_{p,q} w_{pq} \op{p}{q}
  \to \v{\m w} \equiv \flat\m w
  \equiv \sum_{p<q} w_{pq} \ket{\set{p,q}},
\end{align}
where we label basis of vectors $\ket{\set{p,q}}\in\RR^{N\choose 2}$
by a choice of two distinct integers $p,q\in\ZZ_N$.  We similarly
define the ${N \choose 2}\times{N \choose 2}$ matrix
\begin{align}
  \check{\m h} = 2\sum_{p<q} \bar h_{pq} \op{\set{p,q}}
  + \sum_{p<q} \ket{\set{p,q}} \sum_{k\notin\set{p,q}}
  \p{h_{pk} \bra{\set{k,q}} + h_{kq} \bra{\set{p,k}}}.
  \label{eq:h_super_mat}
\end{align}
The condition in \eqref{eq:cond_2} is then equivalently the eigenvalue
equation
\begin{align}
  \check{\m h} \c \v{\m w} = \Delta\p{\m w} \v{\m w}.
  \label{eq:cond_2_eig}
\end{align}
When the interaction Hamiltonian $H_0$ and perturbation $\V_2\p{\m w}$
are translationally invariant, this eigenvalue problem can be reduced
to that of diagonalizing a matrix of dimensions
$\floor{N/2}\times\floor{N/2}$, as we show in Appendix
\ref{sec:trans_inv}.
